### 2021-06-27 code/manuscript.Rmd
Code style improvements

```{r setup, include=FALSE}
# Load packages
library(MASS)
library(lme4)
library(buildmer)
library(emmeans)
library(bayesplot)
library(brms)
library(parallel)
library(reticulate)
library(magick)
library(papaja)
library(cowplot)
library(scales)
library(tidyverse)
library(magrittr)

@@

# Re-run preprocessing and/or model fitting?
rerun_preprocessing <- FALSE
rerun_model_fitting <- FALSE

@@

# File names for easier I/O
fnames <- list(
  montage = "results/montage.csv",
  objects_per_condition = "results/obj-per-cond.csv",
  trials = "results/trials.csv",
  ave_grand = "results/ave_grand.csv",
  ave_tfr_flat = "results/ave-tfr_flat.csv",
  ave_tfr_diff = "results/ave-tfr_diff.csv",
  models_lme = "results/models_lme.RDS",
  models_brm = paste0(
    "results/model_brm_", c("logRT", "P1", "N170", "N400"), ".RDS"
  ) %>%
    set_names(c("logRT", "P1", "N170", "N400")),
  model_brm_prior = "results/model_brm_prior.RDS"
)
```

@@

# Perform preprocessing for all subjects using MNE-Python (see code/preprocessing.py)
# This will run only if `rerun_preprocessing = TRUE` and if the raw data are available
if (rerun_preprocessing) {

@@

  # Determine number of objects per condition for each participant
  fname_log %>%
    map2(subject_id, pp$read_log) %>%
    bind_rows() %>%
    with(table(subject_id, condition) / 3) %>%
    as.data.frame.matrix() %>%
    rownames_to_column("subject_id") %>%
    write_csv(fnames$objects_per_condition)
}
```

@@

# Read evoked *potentials* for all subjects
fname_ave_tfr = ["data/preprocessed/" + sub + "_ave.csv" for sub in r.subject_id]
evo = [pd.read_csv(fname) for fname in fname_ave_tfr]
evo = pd.concat(evo)

# Average across subjects
id_vars = ["part", "condition", "time"]
evo = evo.groupby(id_vars, as_index=False).mean()
evo.to_csv(r.fnames["ave_grand"], float_format="%.3f", index=False)

# Read evoked *power* for all subjects
fname_ave_tfr = ["data/preprocessed/" + sub + "_tfr-ave.csv" for sub in r.subject_id]
ave_tfr = [pd.read_csv(fname) for fname in fname_ave_tfr]
ave_tfr = pd.concat(ave_tfr)

# Subject 18 is weird!
ave_tfr = ave_tfr[ave_tfr["subject_id"] != "sub-18"]

@@

# Average across subjects and save
id_vars.remove("subject_id")
dfs = [ave_tfr_flat, ave_tfr_diff]
fnames_tfr = [r.fnames["ave_tfr_flat"], r.fnames["ave_tfr_diff"]]
for df, fname in zip(dfs, fnames_tfr):
    df = df.groupby(id_vars, as_index=False).mean()
    df.to_csv(fname, float_format="%.3f", index=False)
del df, dfs, evo, ave_tfr, ave_tfr_diff, ave_tfr_flat
```

```{r, models_lme}
# Compute average number of objects per condition
(objects_per_condition <- read_csv(fnames$objects_per_condition, col_types = cols()) %>%
  summarise(across(.cols = -subject_id, .fns = mean)) %>%
  as.list())

@@

    # Return a list of relevant model outputs
    return(
      list(
        model = build@model,
        anova = build@anova,
        summary = build@summary,
        means = as.data.frame(em$emmeans),
        contrasts = as.data.frame(em$contrasts)
      )
    )
  }) %>%

    # Save
    set_names(dvs) %T>%
    saveRDS(fnames$models_lme) -> models_lme
}
```

```{r models_brm, eval=TRUE}
# Theme for plots
bayesplot_theme_update(text = element_text(family = "Helvetica", size = 10))
color_scheme_set("purple")

@@

# Hypotheses of comparisons for informed vs. naive within each part
hypotheses <- c(
  "posthoc_1" = "condition1 - 2/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
  "posthoc_2" = "condition1 + 1/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
  "posthoc_3" = "condition1 + 1/3 * part1:condition1 + 2/3 * part2:condition1 = 0"
)

@@

  # # Allow sigma to very for each participant
  # formula_dv %<>% bf(sigma ~ 1 + (1 | subject_id))

@@

  # Compute follow-up comparisons with Bayes factors
  hyps <- hypothesis(fit_brm, hypotheses) %>% {
    mutate(.$hypothesis, bf01 = Evid.Ratio, bf10 = 1 / Evid.Ratio, .keep = "unused")
  }

  # Return a list of relevant model outputs
    return(
      list(
        model = fit_brm,
        summary = summary(fit_brm),
        hypotheses = hyps
      )
    )

}) %>%
  set_names(dvs) -> models_brm

@@

bf_bayestest <- bayestestR::bayesfactor(example_model$model)
bf_bayestest
```

```{r fig1, include=TRUE, fig.height=11, fig.cap = "(ref:fig1_caption)"}
# Load montage and evoked data
montage <- read_csv(fnames$montage, col_types = cols())
evokeds <- read_csv(fnames$ave_grand, col_types = cols())

@@

First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded objects from all further analyses when participants classified them as being known in the pre-insight part (i.e., before any keywords were presented). This led to the exclusion of an average of `r format(round(objects_per_condition[["Excl_known"]], 1), nsmall = 1)` objects per participant (= `r percent(objects_per_condition[["Excl_known"]] / 120, accuracy = 0.1)` of all unfamiliar objects). Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analysis was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \@ref(fig:exp1-plot)A). Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if participants indicated knowing what the object was or having an assumption. This was the case for an average of `r format(round(objects_per_condition[["Informed"]], 1), nsmall = 1)` objects per participant (= `r percent(objects_per_condition[["Informed"]]/60, accuracy = 0.1)` of objects presented with matching keywords). Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if participants indicated not knowing what the object was or having rather no assumption. This was the case for an average of `r format(round(objects_per_condition[["Naive"]], 1), nsmall = 1)` objects per participant (= `r percent(objects_per_condition[["Naive"]]/60, accuracy = 0.1)` of objects presented with non-matching keywords). Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts. This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any down-stream effects on the subsequent perception of the objects (post-insight part).

@@

```{r exp1-table, include=TRUE, results="asis"}
# Create table of models for Experiment 1
table_exp1 <- create_table(
  models = models_lme,
  stub_anova = c("Part", "Condition", "Pt. × con."),
  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
  caption = "Results of Linear Mixed-Effects Regression Models for Experiment 1\\smallskip",
  note = "Pt. = part, con. = condition, est. = estimate, CI = 95\\% confidence interval."
)
```

@@

plot_tfr_topo <- function(ave_tfr, limits, tmin, tmax, fmin, fmax, legend) {
  # Average across times and frequencies of interest
  ave_tfr_diff %>%
    # Select time window and frequencies of interest
    filter(time >= tmin & time <= tmax & freq >= fmin & freq <= fmax) %>%
    # Convert to long format
    pivot_longer(-c(part, time, freq), names_to = "electrode", values_to = "power") %>%
    # Create one topoplot per part
    group_by(part) %>%
    group_map(function(data_part, part) {
      data_part %>%
        group_by(electrode) %>%
        summarise(power = mean(power), .groups = "drop") %>%
        inner_join(montage, by = "electrode") %>%
        eegUtils::topoplot(
          limits = limits,
          palette = "viridis",
          contour = FALSE,
          quantity = "power",
          scaling = 0.5
        ) +
        theme(legend.position = "none",)
    }) -> plotlist
  #plotlist <- c(plotlist, list(legend))
  plot_grid(
    NULL,
    plotlist[[1]],
    NULL,
    plotlist[[2]],
    NULL,
    plotlist[[3]],
    nrow = 1,
    rel_widths = c(2, 7, 0, 7, 1, 7))
}

# Bring it all together
plot_grid(
  plot_headings(spacing = c(1, 7, 1, 7, 1, 7)),
  do.call(
    plot_tfr_raster, c(tfoi, list(
      ave_tfr = ave_tfr_flat,
      limits = limits_power,
      label = "All channels,\nall conditions"
    ))
  ),
  do.call(
    plot_tfr_raster, c(tfoi, list(
      ave_tfr = ave_tfr_diff,
      limits = limits_power,
      label = "All channels,\n\u0394 (informed - naive)"
    ))
  ),
  do.call(
    plot_tfr_topo, c(tfoi, list(
      ave_tfr = ave_tfr_diff,
      limits = limits_power,
      legend = current_legend))
  ),
  nrow = 4,
  rel_heights = c(1, 5, 5, 5),
  labels = c("", "A", "B", "C"),
  label_y = c(1, 1.16, 1.1, 1),
  label_fontfamily = "Helvetica"
) +
  draw_plot(current_legend, x = -0.42, y = -0.34) +
  annotate_line(0.344, 0.344, -Inf, Inf) +
  annotate_line(0.676, 0.676, -Inf, Inf) +
  ggsave("data/processed/tfr.pdf", width = unit(10, "cm"), height = unit(7, "cm"), device = cairo_pdf)
```

@@

```{r exp2-models, eval=rerun_models}
# Load preprocessed single-trial data
read_tsv("data/processed/exp2-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> data_exp2

@@

# Load preprocessed single-trial data
read_tsv("data/processed/exp2-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) -> data_exp2

@@

```{r exp2-plot, include=TRUE, fig.height=7.5, fig.cap = "(ref:fig2_caption)"}
# Create plot for Experiment 2
plot_grid(
  #plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
  plot_headings(spacing = c(10, 1, 10, 1, 10)),
  plot_erps(comps = comps, evokeds = evokeds_exp2, models = models_exp2, montage = montage),
  plot_legends_erps(direction = "horizontal"),
  nrow = 3, rel_heights = c(0.3, 6, 1.2), labels = NULL
) + # Add some lines (to separate the parts)
  annotate_line(x = 0.328, xend = 0.328, y = 0.15, yend = Inf) +
  annotate_line(x = 0.672, xend = 0.672, y = 0.15, yend = Inf)
```

@@

```{r control-table}
# Calculate average number of objects per condition in Experiments 1 and 2
(stims_joint <- (objects_per_condition + objects_exp2) / 2)

>>>>

```{r, setup, include=FALSE}
# Load packages
library(MASS)
library(lme4)
library(buildmer)
library(emmeans)
library(bayesplot)
library(brms)
library(parallel)
library(reticulate)
library(magick)
library(papaja)
library(cowplot)
library(scales)
library(tidyverse)
library(magrittr)

@@

# Re-run preprocessing and/or model fitting?
rerun_preprocessing <- TRUE
rerun_model_fitting <- TRUE

@@

# File names for easier I/O
dvs <- c("logRT", "P1", "N170", "N400")
fnames <- list(
  montage = "results/montage.csv",
  obj_per_cond = "results/obj-per-cond.csv",
  trials = "results/trials.csv",
  ave_grand = "results/ave_grand.csv",
  ave_tfr_flat = "results/ave-tfr_flat.csv",
  ave_tfr_diff = "results/ave-tfr_diff.csv",
  models_lme = "results/models_lme.RDS",
  models_brm = paste0("results/model_brm_", dvs, ".RDS") %>% set_names(dvs),
  model_brm_prior = "results/model_brm_prior.RDS"
)
```

@@

# Run preprocessing for all subjects using MNE-Python (see preprocessing.py)
# Will run only if `rerun_preprocessing = TRUE` and if raw data are available
if (rerun_preprocessing) {

@@

  # Determine number of objects per condition for each participant
  fname_log %>%
    map2(subject_id, pp$read_log) %>%
    bind_rows() %>%
    with(table(subject_id, condition) / 3) %>%
    as.data.frame.matrix() %>%
    rownames_to_column("subject_id") %>%
    write_csv(fnames$obj_per_cond)
}
```

@@

# Read evoked *potentials* for all subjects
ave = [f"data/preprocessed/{sub}_ave.csv" for sub in r.subject_id]
ave = [pd.read_csv(fname) for fname in fname_ave]
ave = pd.concat(ave)

# Average across subjects
id_vars = ["part", "condition", "time"]
ave = ave.groupby(id_vars, as_index=False).mean()
ave.to_csv(r.fnames["ave_grand"], float_format="%.3f", index=False)

# Read evoked *power* for all subjects
ave_tfr = [f"data/preprocessed/{sub}_tfr-ave.csv" for sub in r.subject_id]
ave_tfr = [pd.read_csv(fname) for fname in fname_ave_tfr]
ave_tfr = pd.concat(ave_tfr)

# # Subject 18 is weird!
# ave_tfr = ave_tfr[ave_tfr["subject_id"] != "sub-18"]

@@

# Average across subjects and save
id_vars.remove("subject_id")
dfs = [ave_tfr_flat, ave_tfr_diff]
fnames_tfr = [r.fnames["ave_tfr_flat"], r.fnames["ave_tfr_diff"]]
for df, fname in zip(dfs, fnames_tfr):
    df = df.groupby(id_vars, as_index=False).mean()
    df.to_csv(fname, float_format="%.3f", index=False)
del df, dfs, ave, ave_tfr, ave_tfr_diff, ave_tfr_flat
```

```{r, models_lme}
# Compute average number of objects per condition
(obj_per_cond <- read_csv(fnames$obj_per_cond, col_types = cols()) %>%
  summarise(across(.cols = -subject_id, .fns = mean)) %>%
  as.list())

@@

    # Return a list of relevant model outputs
    return(
      list(
        model = build@model,
        anova = build@anova,
        summary = build@summary,
        means = as.data.frame(em$emmeans),
        contrasts = as.data.frame(em$contrasts)
      )
    )
  }) %>%
    # Save
    set_names(dvs) %T>%
    saveRDS(fnames$models_lme) -> models_lme
}
```

```{r, models_brm}
# Theme for plots
bayesplot_theme_update(text = element_text(family = "Helvetica", size = 10))
color_scheme_set("purple")

@@

# Hypotheses of comparisons for informed vs. naive within each part
hypotheses <- c(
  "I" = "condition1 - 2/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
  "II" = "condition1 + 1/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
  "III" = "condition1 + 1/3 * part1:condition1 + 2/3 * part2:condition1 = 0"
)

@@

@@

  # Compute follow-up comparisons with Bayes factors
  hyps <- hypothesis(fit_brm, hypotheses) %>% {
    mutate(
      .$hypothesis,
      bf01 = Evid.Ratio, bf10 = 1 / Evid.Ratio, .keep = "unused"
    )
  }

  # Return a list of relevant model outputs
  return(
    list(
      model = fit_brm,
      summary = summary(fit_brm),
      hypotheses = hyps
    )
  )
}) %>%
  set_names(dvs) -> models_brm

@@

# bf_bayestest <- bayestestR::bayesfactor(example_model$model)
# bf_bayestest
```

```{r, fig1, include=TRUE, fig.height=11, fig.cap = "(ref:fig1_caption)"}
# Load montage and evoked data
montage <- read_csv(fnames$montage, col_types = cols())
evokeds <- read_csv(fnames$ave_grand, col_types = cols())

@@

First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded objects from all further analyses when participants classified them as being known in the pre-insight part (i.e., before any keywords were presented). This led to the exclusion of an average of `r format(round(obj_per_cond[["Excl_known"]], 1), nsmall = 1)` objects per participant (= `r percent(obj_per_cond[["Excl_known"]] / 120, accuracy = 0.1)` of all unfamiliar objects). Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analysis was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \@ref(fig:exp1-plot)A). Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if participants indicated knowing what the object was or having an assumption. This was the case for an average of `r format(round(obj_per_cond[["Informed"]], 1), nsmall = 1)` objects per participant (= `r percent(obj_per_cond[["Informed"]]/60, accuracy = 0.1)` of objects presented with matching keywords). Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if participants indicated not knowing what the object was or having rather no assumption. This was the case for an average of `r format(round(obj_per_cond[["Naive"]], 1), nsmall = 1)` objects per participant (= `r percent(obj_per_cond[["Naive"]]/60, accuracy = 0.1)` of objects presented with non-matching keywords). Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts. This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any down-stream effects on the subsequent perception of the objects (post-insight part).

@@

```{r, tab1, include=TRUE, results="asis"}
# Create table of models for Experiment 1
table_exp1 <- create_table(
  models = models_lme,
  stub_anova = c("Part", "Condition", "Pt. × con."),
  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
  caption = paste(
    "Linear Mixed-Effects Regression Models for Experiment 1",
    "\\smallskip"
  ),
  note = paste(
    "Pt. = part, con. = condition, est. = estimate, CI = 95\\%",
    "confidence interval."
  )
)
```

@@

plot_tfr_topo <- function(ave_tfr, limits, tmin, tmax, fmin, fmax, legend) {
  # Average across times and frequencies of interest
  ave_tfr_diff %>%
    # Select time window and frequencies of interest
    filter(time >= tmin & time <= tmax & freq >= fmin & freq <= fmax) %>%
    # Convert to long format
    pivot_longer(-c(part, time, freq), names_to = "electrode", values_to = "power") %>%
    # Create one topoplot per part
    group_by(part) %>%
    group_map(function(data_part, part) {
      data_part %>%
        group_by(electrode) %>%
        summarise(power = mean(power), .groups = "drop") %>%
        inner_join(montage, by = "electrode") %>%
        eegUtils::topoplot(
          limits = limits,
          palette = "viridis",
          contour = FALSE,
          quantity = "power",
          scaling = 0.5
        ) +
        theme(legend.position = "none", )
    }) -> plotlist
  # plotlist <- c(plotlist, list(legend))
  plot_grid(
    NULL,
    plotlist[[1]],
    NULL,
    plotlist[[2]],
    NULL,
    plotlist[[3]],
    nrow = 1,
    rel_widths = c(2, 7, 0, 7, 1, 7)
  )
}

# Bring it all together
plot_grid(
  plot_headings(spacing = c(1, 7, 1, 7, 1, 7)),
  do.call(
    plot_tfr_raster, c(tfoi, list(
      ave_tfr = ave_tfr_flat,
      limits = limits_power,
      label = "All channels,\nall conditions"
    ))
  ),
  do.call(
    plot_tfr_raster, c(tfoi, list(
      ave_tfr = ave_tfr_diff,
      limits = limits_power,
      label = "All channels,\n\u0394 (informed - naive)"
    ))
  ),
  do.call(
    plot_tfr_topo, c(tfoi, list(
      ave_tfr = ave_tfr_diff,
      limits = limits_power,
      legend = current_legend
    ))
  ),
  nrow = 4,
  rel_heights = c(1, 5, 5, 5),
  labels = c("", "A", "B", "C"),
  label_y = c(1, 1.16, 1.1, 1),
  label_fontfamily = "Helvetica"
) +
  draw_plot(current_legend, x = -0.42, y = -0.34) +
  annotate_line(0.344, 0.344, -Inf, Inf) +
  annotate_line(0.676, 0.676, -Inf, Inf) +
  ggsave("data/processed/tfr.pdf", width = unit(10, "cm"), height = unit(7, "cm"), device = cairo_pdf)
```

@@

```{r exp2-models, eval=rerun_models}
# Load preprocessed single-trial data
read_tsv("data/processed/exp2-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
    )),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> data_exp2

@@

# Load preprocessed single-trial data
read_tsv("data/processed/exp2-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
    )),
    participant = factor(participant),
    item = factor(item)
  ) -> data_exp2

@@

```{r exp2-plot, include=TRUE, fig.height=7.5, fig.cap = "(ref:fig2_caption)"}
# Create plot for Experiment 2
plot_grid(
  # plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
  plot_headings(spacing = c(10, 1, 10, 1, 10)),
  plot_erps(comps = comps, evokeds = evokeds_exp2, models = models_exp2, montage = montage),
  plot_legends_erps(direction = "horizontal"),
  nrow = 3, rel_heights = c(0.3, 6, 1.2), labels = NULL
) + # Add some lines (to separate the parts)
  annotate_line(x = 0.328, xend = 0.328, y = 0.15, yend = Inf) +
  annotate_line(x = 0.672, xend = 0.672, y = 0.15, yend = Inf)
```

@@

```{r control-table}
# Calculate average number of objects per condition in Experiments 1 and 2
(stims_joint <- (obj_per_cond + objects_exp2) / 2)
